Towards Proof-Reconstruction of Problems in Classical Propositional Logic

### 2017-10-18 paper/sections/acknowledgements.tex

I would like to thank to Universidad EAFIT in Medell\'in, Colombia for funding
support of this research and my master studies.
This project was a product of the Logic and Computation
Research Group at Universidad EAFIT.
My special thanks to Andrés Sicard-Ramiréz for its patience, valuable comments
during this research, and in general advices and discussions around many
topics of my interest.

>>>>

I would like to thank to Universidad EAFIT in Medell\'in, Colombia for funding
support of this research and my master studies.
This project was a product of the Logic and Computation
Research Group at Universidad EAFIT.
My special thanks to Andrés Sicard-Ramiréz to give me the opportunity
to work on these exciting topics but also for its patience, discussions,
and very valuable comments during all this research.

### 2017-10-18 paper/sections/metis-language-and-proofs.tex
[ paper ] lots of grammar fixes.

The \TPTP language --which includes the first-order
form (denoted by \name{fof}) and clause normal form (denoted by
\name{cnf}) formats~\cite{sutcliffe2009} -- is de facto input
standard language to encode problems for many \ATPs. The \TPTP
syntax describes a well-defined grammar to handle annotated formulas
with the following form.

@@

The \TSTP language is de facto output standard language
for derivations of ATPs~\cite{Sutcliffe-Schulz-Claessen-VanGelder-2006}.
A \TSTP derivation is a directed acyclic graph, a proof tree,
where each leaf is a formula from the \TPTP input. A node is a formula
inferred from the parent formulas. The root is the final derived formula,
such a derivation is a list of annotated formulas with the form.

>>>>

The \TPTP language --which includes the first-order
form (denoted by \name{fof}) and clause normal form (denoted by
\name{cnf}) formats~\cite{sutcliffe2009,Sicard-Ramirez2016} -- is de facto input
standard language to encode problems for many \ATPs. The \TPTP
syntax describes a well-defined grammar to handle annotated formulas
with the following form.

@@

The \TSTP language is de facto output standard language
for derivations of ATPs~\cite{Sutcliffe-Schulz-Claessen-VanGelder-2006,Sicard-Ramirez2016}.
A \TSTP derivation is a directed acyclic graph, a proof tree,
where each leaf is a formula from the \TPTP input. A node is a formula
inferred from the parent formulas. The root is the final derived formula,
such a derivation is a list of annotated formulas with the form.

### 2017-10-18 paper/sections/related-work.tex

@@

\name{Waldmeister} is an automatic theorem prover for unit
equational logic \cite{hillenbrand1997}.
\citeauthor{foster2011integrating}~\cite{foster2011integrating}
integrate \name{Waldmeister} into \Agda
\cite{agdateam}. This integration requires a proof-reconstruction
step, but authors' approach is restricted to pure equational logic
--also called identity theory~\cite{humberstone2011}-- that is,
first-order logic with equality but no other predicate symbols and
no functions symbols~\cite{appel1959}.

>>>>

In this section, we present an extended version of the related work description made in the proposal for this research~\cite{Sicard-Ramirez2016}.

@@

\name{Waldmeister} is an automatic theorem prover for unit
equational logic \cite{hillenbrand1997}.
\citeauthor{foster2011integrating}~\cite{foster2011integrating}
integrate \name{Waldmeister} into \Agda
\cite{agdateam}. This integration requires a proof-reconstruction
step, but authors' approach is restricted to pure equation logic
--also called identity theory~\cite{humberstone2011}-- that is,
first-order logic with equality but no other predicate symbols and
no functions symbols~\cite{appel1959}.
